Data Analysis and Visualisation using R

### 2016-01-12 paper.tex
Finish elder

@@

>>>>

\subsection{Elder subset}

We start exploring this set of data by plotting a scatterplot between {\tt Y} and {\tt X7}, the only remaining predictor. We observe that a funnel shape formed by the data points overshadows an upward linear relationship, as shown in Figure~\ref{fig:03-elder}. The funnel shape may imply a non-constant variance in the error terms, a phenomenon called {\em heteroscedasticity}. In this data set, heteroscedasticity causes the variance in error terms increases with the response values. One possible solution is transforming the response variable using a concave function hence we compare three models: $Y \sim X7$, $log(Y) \sim X7$ and $\sqrt{Y} \sim X7$. The funnel-shaped pattern and magnitude observed in the residuals versus fitted values plot for the simple linear regression model has been greatly reduced in Figure~\ref{fig:04-elder}, although not completely eliminated, through the use of concave transformation. The training $R^2$ values for these models are 0.3359, 0.3305 and 0.3373 respectively. Based on this, we have chosen $sqrt{Y} \sim X7$ as the resulting linear regression coefficients are significant.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{project/images/03-elder.png}
  \caption{Inspection plot for heteroscedasticity in elder dataset.}
  \label{fig:03-elder}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{project/images/04-elder.png}
  \caption{Inspection plots showing reduced funnel-shape residuals for $\sqrt{Y} \sim X7$ in elder dataset.}
  \label{fig:04-elder}
\end{figure}

@@

\lstinputlisting[breaklines=true,language=R,caption={elder.R},label=elder]{project/5-elder.R}
